Galaxy Zoo: Morphological Classifications for 150,000 Galaxies in HST Legacy Imaging

### 2016-04-30 writeup/gz_hubble_data.tex
added average goodness of fit values to high order tasks in ferengi to section 4

In the FERENGI data, these numbers severely limit the amount of information we can extract for the higher-tier questions. The debiasing technique used (Section~\ref{ssec:zeta}) require that at least 10~users answer each question for a galaxy image at $z=0.3$ \emph{and} its image at higher redshift. This requirement is by default met by all galaxies when analyzing the first question, since it is asked of all users. This requirement is often \emph{not} met for questions beyond Task~01; on average 59\% of the galaxies do not have sufficient data to measure a correction, as compared to 2\% acheived for Task~01 (see Table~\ref{tbl:ferengi_corrections}). Of the remaining FERENGI galaxies which did meet this requirement, the data available in each redshift-surface brightness bin were not tightly correlated between $p_{task,z=0.3}$ and $p_{task,z}$, and relationships between the two could not be fit with high confidence. We use these galaxies to compute $\zeta$ for each Task, and find the p-values for the resulting functions between $placeholder < p < placeholder$, which we consider insufficient for deriving a correction. We show an example of this in Section \ref{sec:ferengi_bar}, where we show results of measuring $\zeta$ for $p_{\rm bar}$ in Task~03. For this reason we only offer debiased vote fractions for Task~01 (smooth/features/artifact).

>>>>

In the FERENGI data, these numbers severely limit the amount of information we can extract for the higher-tier questions. The debiasing technique used (Section~\ref{ssec:zeta}) require that at least 10~users answer each question for a galaxy image at $z=0.3$ \emph{and} its image at higher redshift. This requirement is by default met by all galaxies when analyzing the first question, since it is asked of all users. This requirement is often \emph{not} met for questions beyond Task~01; on average 60.0\% of the galaxies do not have sufficient data to measure a correction, as compared to 2.0\% acheived for Task~01 (see Table~\ref{tbl:ferengi_corrections}). Of the remaining FERENGI galaxies which did meet this requirement, polynomials were fit to the data in each redshift-surface brightness bin, as was done for Task~01 (described above). The goodness-of-fit was evaluated in each bin, for each Task, using the value of the sum of the square residuals (SSR). The mean SSR for all Tasks was $\mu_{\rm SSR}$ = 0.46 $\pm$ 0.36, which was not considered sufficiently low in any Task for the fits to accurately model the data. An example of the debiasing technique applied to $p_{\rm bar}$ is shown in Section \ref{sec:ferengi_bar}; visual inspection of Figure~\ref{fig:p_vs_p_bar} confirms the available data in each bin is scattered to a degree at which no correlation may be confidentely obtained. For these reasons, debiased vote fractions are only offered for Task~01 (smooth/features).
